---
title: "newassignment1"
author: "Xiang Li"
date: "9/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```
#Import the database and then choose the data needed to be anylized.
#mtcars
#Format
#A data frame with 32 observations on 11 (numeric) variables.
#[, 1]	mpg	Miles/(US) gallon
#[, 2]	cyl	Number of cylinders
#[, 3]	disp	Displacement (cu.in.)
#[, 4]	hp	Gross horsepower
#[, 5]	drat	Rear axle ratio
#[, 6]	wt	Weight (1000 lbs)
#[, 7]	qsec	1/4 mile time
#[, 8]	vs	Engine (0 = V-shaped, 1 = straight)
#[, 9]	am	Transmission (0 = automatic, 1 = manual)
#[,10]	gear	Number of forward gears
#[,11]	carb	Number of carburetors
```{r}
# call built-in data mtcars.
data(mtcars)
# Select only car models where mpg<20
mtcars_mpg2 <- mtcars[mtcars$mpg < 20,]
# Reduce the variables to mpg, cyl, disp, hp, gears
mtcars_mpg2 <- mtcars_mpg2[, c(1,2,3,4,10)]
```

#Use the function from hand_function.R
```{r}
# read the R file hand_functions.R so that it can be used
# notice that with echo = TRUE 
source(file = "hand_functions.R", echo = TRUE)

# Now use the function from hand_functions.R
sp_out <- sum_special(mtcars_mpg2)
```

#Plot mtcars with selected data to illustrate that how doess the mpg changing trend while displacement is iincreasing.
#theme_minimal() :A minimalistic theme with no background annotations.
#theme_classic(): A classic-looking theme, with x and y axis lines and no gridlines.
```{r}
ggplot(mtcars_mpg2) +
  aes(x = disp, y = mpg) +
  geom_point(shape = "bullet", size = 4L, colour = "#B22222") +
  geom_smooth(span = 0.5)+
  theme_minimal()
```
```{r}
#library(esquisse)
#mtcars_mpg2<-mtcars[as.factor(mtcars$cyl)]
#esquisser(mtcars_mpg2)
```
# note that this boxplot cannot be made with esquisse() unless
# the data is adjusted.  What adjustment is needed? 

#ANSWER: Use as.factor(cyl) insteal of cyl becasue a boxplot is a method for graphically depicting groups of numerical data through their quartiles. Therefore, I need to use as.factor to change cyl to a classification variable.

```{r}

ggplot(mtcars_mpg2, aes(x=as.factor(cyl), y=mpg)) + 
  geom_boxplot(fill="slateblue", alpha=0.2) + 
  xlab("cyl")

```

